---
title: "T-Test for a One-Time Series for Stock Data"
output: html_notebook
---

```{r}
library(quantmod)
```

# High t-value, reject the null hypothesis
# Lower p-value, reject the null hypothesis
# value falls outside the confidence interval, reject the null hypothesis

```{r}
amd <- getSymbols("AMD", from = "2020-01-01", to = "2020-06-25", auto.assign = F)
```


```{r}
head(amd)
```

```{r}
tail(amd)
```
```{r}
amd$AMD.Adjusted
```
```{r}
close <- amd$AMD.Adjusted
head(close)
```
```{r}
ret <- diff(log(close))
tail(ret)
```
```{r}
t.test(ret, mu=0)
```
# The degree of freddom of 372, the critical value is close to a normal distribution (T = 1.96).
# When the value is higher than 1.96, we reject the underlying hypothesis or we accept the hypothesis.
# t-value is 0.83876 is lower than 1.96, we accept the hypthesis.
# Rule of thumb: t-value is less than 2, we accept.
# p-value is 0.4021 and is 40.21%; therefore, is more than 5% and we accept hypothesis.
# 0 is in the range, we accept hypothesis.
